Call Center Regression Data Analysis

### 2022-11-30 References/Manuscript.tex
commit #methods cleanup

Here we do not see any clear pattern based on whether its winter, spring, summer, or fall. Overall, this was not too surpising.

I also created linear models to show the relationship between calls per agent and average waitime, holdtime, average goal met, and average 
interaction value. Average goal met was a variable created in relationship to the AnsweredGoalMet. AnsweredGoalMet was given in 1 and 0s, 
1 if the goal was hit and 0 if it was not hit. This variable is very fluid, as each company has its own reasoning for what they want their
goal time to be. Average Interaction Value was based off a variable that was created based on the InteractionOutcome. "Handled "got assigned 
1 as it was a positive outcome and -1 for "Abandoned" and "Leave Number" as they were deemed negative. The others were considered neutral, for example
"Not Specified", was given a 0.

@@

To prevent this, I soley focus on one variable at a time when making my models on agents. Homoscedasticity is an assumption there is equal or similar variances in different groups being compared.
Logistic and Linear Regression Assumptions: Violation Recognition and Control goes into detail about this stating, "it is necessary to make a note about sample size for this type of regression model. In Linear

@@

lowest staffed day of the week. A possible suggestion to the company would be add an agent on Friday. Members may be calling about last minute

@@

consistant in all aspects. Note that the reason why the "num15minPeriods" variable is not the same is due to the outliers in the dataset where individuals

>>>>

Here we do not see any clear pattern based on whether its winter, spring, summer, or fall. Overall, this was not too surpising as this confirms my previous findings.

I also created linear models to show the relationship between calls per agent and average waitime, holdtime, average goal met, and average 
interaction value. Average goal met was a variable created in relationship to the AnsweredGoalMet. AnsweredGoalMet was given in 1 and 0s, 
1 if the goal was hit and 0 if it was not hit. This variable is very fluid, as each company has its own reasoning for what they want their
goal time to be. Average Interaction Value was based off a variable that was created based on the InteractionOutcome. "Handled" was assigned 
1 as it was a positive outcome and -1 for "Abandoned" and "Leave Number" as they were deemed negative. The others were considered neutral, for example
"Not Specified", was given a 0.

@@

To prevent this, I soley focused on one variable at a time when making my models on agents. Homoscedasticity is an assumption there is equal or similar variances in different groups being compared.
"Logistic and Linear Regression Assumptions: Violation Recognition and Control" goes into detail about this stating, "it is necessary to make a note about sample size for this type of regression model. In Linear

@@

lowest staffed day of the week. I would possibly suggest to the company that they should add an agent on Fridays. Members may be calling about last minute

@@

consistant in all aspects. Note that the reason why the "Num15minPeriods" variable is not the same is due to the outliers in the dataset where individuals
